Variability of Planetary Mass Companion 2M1207 B

### 2015-08-19 summary/letter/letter_v1.tex
let's do another mc fit

\section{Observation}
We took high contrast direct imaging observation of 2M1207 system on
UT 2014 April 11 using HST.  (\textit{HST} Proposal GO-13418, PI:
D. Apai). The data were acquired with the Wide Field Camera 3 (WFC3)
in filter F125W ($\lambda_{\mbox{pivot}}$ = 1245.9 nm. FWHM = 301.5
nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM = 287.9 nm)
using the $256\times256$ sub-array mode. We observed 2M1207 system in
six contiguous HST orbits and obtained a data-set that have a temporal
resolution of $\sim1.5$ minutes and baseline of 8 hours and 40
minutes, interrupted by Earth occultaions of 58 minutes every  94 minutes.

The observations was initially designed to apply two-roll
PSF-subtraction (e.g. \cite{Song2006}) to remove the background light from the primary star. The
telescope roll angles for data taken in orbit 1, 3, 5 and those taken
in orbit 2, 4, 6 differed by $25^{\circ}$, thus the roll displacement
of the companion is 0.34 .  In
each orbit we took a sequence of 13 SPARS25 exposures with NSAMP=10,
alternating between F160W and F125W filters, with 2-3 identical
exposures in one exposure sequence. To improve PSF sampling and reduce
the risk caused by bad pixels, we applied standard 4 point
dithering. In each orbit, exposures were taken with dithering position
1 -- 4 sequently. To sum, we obtained 70 multi-acuum images for filter
F125W and 64 images for filter F160W with exposure time of 88.4
seconds for both two filters.

@@

\subsubsection{White noise}
The difficulties of high contrast photometry is finally exhibited by
the error bars of the measurement. The scatterings of the photometric
measurements are dominated by photon noise.  We estimated the photon
noise by calculating the total flux within a 3-pixel (0.39 arcsec)
aperture centered on 2M1207 B. The photon noises for F125W and F160W photometry are
2.1\% and 1.2\%. These calculation results are at the same level of
the scattering of the photometric time series.

@@

Flat field uncertainties have smaller effects on PSF photometry since
multiple pixels are fitted simultaneously. To verify this, we multiplied
an artificial flat field error mask that is a uniform distributed
Gaussian noise array with mean of 1 and sigma of 1\% to every image,
and repeat the PSF photometry routine with the error-applied
images. We obtained almost same photometry measurements as the
original.

>>>>

\section{Observation}
We took high contrast direct imaging observation of 2M1207 system on
UT 2014 April 11 using HST.  (\textit{HST} Proposal GO-13418, PI:
D. Apai). The data were acquired with the Wide Field Camera 3 (WFC3)
in filter F125W ($\lambda_{\mbox{pivot}}$ = 1245.9 nm, full width at
half maximum (FWHM) = 301.5
nm) and F160W ($\lambda_{\mbox{pivot}}$ 1540.52, FWHM = 287.9 nm)
using the $256\times256$ sub-array mode. We observed 2M1207 system in
six contiguous HST orbits and obtained a data-set that have a temporal
resolution of $\sim1.5$ minutes and baseline of 8 hours and 40
minutes, interrupted by Earth occultaions of 58 minutes every  94 minutes.

The observations was initially designed to apply two-roll
point spread function (PSF) subtraction (e.g. \cite{Song2006}) to remove the background light
from the primary star. The telescope roll angles for data taken in
orbit 1, 3, 5 and those taken in orbit 2, 4, 6 differed by
$25^{\circ}$, thus the roll displacement of the companion is $0.34''$
that is 2.75 and 2.30 resolution elements in F125W and F160W respectively.
In each orbit we took a sequence of 13 SPARS10 exposures with
NSAMP=10, alternating between F160W and F125W filters, with 2-3
identical exposures in one exposure sequence. To improve PSF sampling
and reduce the risk caused by bad pixels, we applied standard 4 point
dithering. In each orbit, exposures were taken with dithering position
1 -- 4 sequently. Over the 6 orbits, we obtained 70 multi-acuum images for filter
F125W and 64 images for filter F160W with exposure time of 88.4
seconds for both two filters.

@@

\subsubsection{White noise}
The scatters of the photometric measurements are dominated by photon
noise. Uncertainties of one photometric measurement was combined by
photon noise of every pixel during the PSF fit. The photon noises for
2M1207B photometry in F125W and F160W are 1.33\% and 1.02\%,
respectively, and are at the same level of the scatter of the
photometric time series.

@@

Flat field uncertainties have smaller effects on PSF photometry than
aperture photometry since multiple pixels are fitted
simultaneously. To verify this, we multiplied an artificial flat field
error mask that is a uniform distributed Gaussian noise array with
mean of 1 and sigma of 1\% to every image, and repeat the PSF
photometry routine with the error-applied images. We obtained almost
same photometry measurements as the original.
